A Linear Solution of the Linearity Challenge

### 2025-12-13 paper/Safety.lagda.tex
restored safety

\begin{code}[hide]
{-# OPTIONS --rewriting #-}
open import Data.List.Base using ([]; _∷_; [_])

@@

\begin{code}
data ReductionContext (Δ : Context) : Context → Set where
  hole   : ReductionContext Δ Δ
  cut-l  : ∀{Γ Γ₁ Γ₂ A} (p : Γ ≃ Γ₁ + Γ₂) →
           ReductionContext Δ (A ∷ Γ₁) → Process (dual A ∷ Γ₂) →
           ReductionContext Δ Γ
  cut-r  : ∀{Γ Γ₁ Γ₂ A} (p : Γ ≃ Γ₁ + Γ₂) →
           Process (A ∷ Γ₁) → ReductionContext Δ (dual A ∷ Γ₂) →
           ReductionContext Δ Γ
\end{code}

@@

\begin{code}
_⟦_⟧ : ∀{Γ Δ} → ReductionContext Δ Γ → Process Δ → Process Γ
hole ⟦ P ⟧         = P
cut-l p 𝒞 Q ⟦ P ⟧  = cut p (𝒞 ⟦ P ⟧) Q
cut-r p Q 𝒞 ⟦ P ⟧  = cut p Q (𝒞 ⟦ P ⟧)
\end{code}

@@

\begin{code}
WellFormed        : ∀{Γ} → Process Γ → Set
WellFormed {Γ} P  = ∀{Δ} {𝒞 : ReductionContext Δ Γ} {Q : Process Δ} →
                   P ⊒ (𝒞 ⟦ Q ⟧) → Alive Q
\end{code}

@@

\begin{code}
type-safety : ∀{Γ} (P : Process Γ) → WellFormed P
type-safety P {_} {_} {Q} _ = deadlock-freedom Q
\end{code}

>>>>

\begin{code}[hide]
{-# OPTIONS --rewriting #-}
open import Data.List.Base using ([]; _∷_; [_])
open import Relation.Unary

@@

\begin{code}
data ReductionContext (Δ : Context) : Context → Set where
  hole   : ReductionContext Δ Δ
  cut-l  : ∀{A} → ∀[  ((A ∷_) ⊢ ReductionContext Δ) ∗ ((dual A ∷_) ⊢ Proc) ⇒
                      ReductionContext Δ ]
  cut-r  : ∀{A} → ∀[  ((A ∷_) ⊢ Proc) ∗ ((dual A ∷_) ⊢ ReductionContext Δ) ⇒
                      ReductionContext Δ ]
\end{code}

@@

\begin{code}
_⟦_⟧ : ∀{Γ Δ} → ReductionContext Δ Γ → Proc Δ → Proc Γ
hole               ⟦ P ⟧ = P
cut-l (𝒞 ⟨ p ⟩ Q)  ⟦ P ⟧ = cut ((𝒞 ⟦ P ⟧) ⟨ p ⟩ Q)
cut-r (Q ⟨ p ⟩ 𝒞)  ⟦ P ⟧ = cut (Q ⟨ p ⟩ (𝒞 ⟦ P ⟧))
\end{code}

@@

\begin{code}
WellFormed : ∀{Γ} → Proc Γ → Set
WellFormed {Γ} P = ∀{Δ} {𝒞 : ReductionContext Δ Γ} {Q : Proc Δ} →
                   P ⊒ (𝒞 ⟦ Q ⟧) → Alive Q
\end{code}

@@

\begin{code}
type-safety : ∀{Γ} (P : Proc Γ) → WellFormed P
type-safety P {_} {_} {Q} _ = deadlock-freedom Q
\end{code}
